### 2014-02-18 thesis/src/chapters/chapter-adaptivity.tex
Thesis: Adaptivity

\section{Self-manageable system}

@@

As  \cite{murch2004autonomic} explains, there are four levels of a system manageability maturity. The higher the level, the better it manages itself leading to a adaptive or autonomic system at best:
\begin{itemize}
 \item \emph{Basic} - IT professionals manage each system element. Activities related to configuration, optimisation, healing, and protection of IT infrastructure components are performed manually.
 \item \emph{Managed} - System management technologies can be used to collect information from different systems and analyze this information. In this scenario, IT professionals do most of the analysis, but it is a starting point for the automation of IT tasks.
 \item \emph{Predictive} - Individual components monitor themselves, analyze changes and offer advice. Therefore, dependency on people is reduced and decision-making is improved.
 \item \emph{Adaptive} - IT components can, individually or group-wise, monitor, analyze operations and offer advice with minimal human intervention.
 \item \emph{Autonomic} - System operations are managed by business policies established by the administrator. In fact, business policy drives overall IT management, while at the adaptive level; there is an interaction between humans and the system.
\end{itemize}

>>>>

\section{Self-adaptive system}

@@
